quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-15 paper-quollr.Rmd
Added show_langevitour projections

```{r, eval=knitr::is_html_output(), out.width="100%", fig.height=5, fig.width=25}
scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

@@

>>>>

```{r, eval=knitr::is_latex_output(), out.width="100%", fig.height=5, fig.width=25}
scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

@@

```{r, eval=knitr::is_latex_output()}
scurve_proj_umap_model1 + scurve_proj_umap_model2 + scurve_proj_umap_model3 + scurve_proj_umap_model4 + 
  plot_layout(ncol = 4)
```
